Hierarchical Dispatching and Overriding

### 2017-06-17 Aplas17/sections/Formalization.tex
separate \overline

\begin{figure*}[t]
\begin{displaymath}
\begin{array}{l}
\begin{array}{llrl}
\text{Interfaces}   & IL & \Coloneqq & \interface{I}{I}{M} \\
\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I_x}{x}{J}{e} \\
\text{Expressions}  & e  & \Coloneqq & x \mid
e.m(\overline{e}) \mid
\new{I} \mid
e.I::m(\overline{e}) \mid
\kwsuper.I::m(e) \; \mid \; \angl{I}e \\
\text{Context}      & \Gamma & \Coloneqq & \overline{x:I} \\
\text{Values}       & v & \Coloneqq & \angl{I} \new{J} \\
%%\\
%%\text{Interface names} & I, J, K & & \\
%%\text{Method names} & m & & \\
%%\text{Variable names} & x & &
\end{array}
\end{array}
\end{displaymath}
\caption{Syntax of \name{}.}\label{fig:syntax}
\end{figure*}

@@

\begin{theorem}[Progress]~\label{theorem_progress}
$\textit{Suppose } e \textit{ is a well-typed expression } $ \\
\begin{enumerate}
\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).m(\overline{\angl{I_E}} \; \overline{e})$ as a subexpression,
    then $ \emph{\mbody}(m, I, J) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).K::m(\overline{\angl{I_E} e})$ as a subexpression,
    then $ \emph{\mbody}(m, I, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
\item If $e$ includes $\emph{\kwsuper}.K::m(\overline{\angl{I_E} e})$ as a subexpression,
    then $ \emph{\mbody}(m, K, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
\end{enumerate}
\end{theorem}
\begin{proof}
See Appendix~\ref{appendix_proof}.
\end{proof}

>>>>

\begin{figure*}[t]
\begin{displaymath}
\begin{array}{l}
\begin{array}{llrl}
\text{Interfaces}   & IL & \Coloneqq & \interface{I}{I}{M} \\
\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I_x}{x}{J}{e} \\
\text{Expressions}  & e  & \Coloneqq & x \mid
e.m(\overline{e}) \mid
\new{I} \mid
e.I::m(\overline{e}) \mid
\kwsuper.I::m(e) \; \mid \; \angl{I}e \\
\text{Context}      & \Gamma & \Coloneqq & \overline{x}:\overline{I} \\
\text{Values}       & v & \Coloneqq & \angl{I} \new{J} \\
%%\\
%%\text{Interface names} & I, J, K & & \\
%%\text{Method names} & m & & \\
%%\text{Variable names} & x & &
\end{array}
\end{array}
\end{displaymath}
\caption{Syntax of \name{}.}\label{fig:syntax}
\end{figure*}

@@

\begin{theorem}[Progress]~\label{theorem_progress}
$\textit{Suppose } e \textit{ is a well-typed expression } $ \\
\begin{enumerate}
\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).m(\overline{\angl{I_E}} \; \overline{e})$ as a subexpression,
    then $ \emph{\mbody}(m, I, J) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).K::m(\overline{\angl{I_E}} \overline{e})$ as a subexpression,
    then $ \emph{\mbody}(m, I, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
\item If $e$ includes $\emph{\kwsuper}.K::m(\overline{\angl{I_E}} \overline{e})$ as a subexpression,
    then $ \emph{\mbody}(m, K, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
\end{enumerate}
\end{theorem}
\begin{proof}
See Appendix~\ref{appendix_proof}.
\end{proof}
